
%%%%%%%%% MASTER -- compiles the sections

\documentclass[12pt,letterpaper]{scrartcl}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
}
\usepackage{setspace}
\usepackage{listings} %for source code figures
\usepackage[toc,xindy,style=long3colheaderborder,footnote]{glossaries}
\addtokomafont{disposition}{\rmfamily}
%\usepackage[toc,xindy]{glossaries}
\makeindex
\makeglossaries

\input{reportGlossary.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}                                                      %%
%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %% (It is recommended that you       %%
\setlength{\evensidemargin}{0in}  %%  not change these parameters,     %%
\setlength{\textheight}{8.5in}    %%  at the risk of having your       %%
\setlength{\topmargin}{0in}       %%  proposal dismissed on the basis  %%
\setlength{\headheight}{0in}      %%  of incorrect formatting!!!)      %%
\setlength{\headsep}{0in}         %%                                   %%
\setlength{\footskip}{.5in}       %%                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                   %%
\newcommand{\required}[1]{\section*{\hfil #1\hfil}}                    %%
\renewcommand{\refname}{\hfil References Cited\hfil}                   %%
\bibliographystyle{plain}                                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%PUT YOUR MACROS HERE

\date{Spring 2012}
\title{Team EcoData\\
}
\subtitle{``Hatch'' Data Management Tool}

\author{Mike Solomon\\
	Colby Blair \\
	Computer Science Undergraduates \\
	University of Idaho Computer Science Department\\
	CS 481 Capstone Project \\
}


\begin{document}

\begin{flushright}
    Team EcoData \\
    CS Department \\
    University of Idaho \\
    May 10, 2012 \\
\end{flushright}

\noindent
Alex Fremier \\
Associate Professor \\
College of Natural Resources \\
University of Idaho

\section*{Letter of Transmittal}

\textbf{To:} Alex Fremier and other interested parties

\noindent
\textbf{Subject:} Hatch data management tool for the College of Natural Resources.

\textbf{Purpose:} This final report discusses the outcome, design, and development of the Hatch data management project.
The goal of the Hatch project is to introduce new approaches to organizing data and making
it more searchable in order to address the challenges of managing data in a scientific research
environment.
The Hatch project creates the foundation for a tool that allows users to upload, search,
format, and visualize their data in ways they didn't think of before. This report highlights some of the 
problems with computation and data management in the current research environment, and makes 
suggestions for new approaches. It talks about specific algorithms for searching data, and standards for
formatting and storing it.

\textbf{Background:} The amount of data being stored in scientific databases today is growing 
exponentially. The amount of available computational power, however, is no longer growing 
exponentially.
The consequence is an gap opening between data and results. Researchers are trying to build and rebuild
their computational infrastructure, to try to get computational growth back to the pace of data growth.
But in this report, we suggest a complimentary approach to computing research data. The Hatch project
comes from the idea that a significant amount of research data is redundant or not wanted. But it is also
vast and currently unmanagable. Researchers end up wasting computation time on data points and sets
that they do not care about, at the expense of ones they do care about.

\textbf{Preliminary Work:} With the experience of the authors of this report, there is more than 8 
years of work in computer science, bioinformatics, and natural resources. There are over 3 years of 
work in computing clusters for the University of Idaho Initiative for Bioinformatics and 
Evolutionary STudies (IBEST), as well as 1.5 years of research in wildlife management.

By making use of these experiences, the EcoData team was able to create an extensible prototype for 
sophisticated scientific data management.

\thispagestyle{empty}

\pagebreak

\maketitle

\thispagestyle{empty}

\pagebreak

\thispagestyle{empty}
\tableofcontents
\listoffigures

\pagebreak

\doublespacing

\section{Executive Summary}
Large amounts of data are often collected for modern scientific projects.  Once this data is 
collected, it must be stored in an accessible location with easy access to tools for information 
management.  Centralized databases often provide storage and access, but do not provide easy-to-use 
data management tools or basic data exploration such as graphing and visualization.

Our primary target is easing the management of large sets of ecological data from projects like 
PTAGIS, which collects information on tagged fish in the Columbia Basin.  Large data sets such as
these require large amounts of processing.  There is a widening gap between the supply of data
and our ability to process it \cite{gordon_moore}.

Clearly, the inability to process scientific data weakens research projects.  The Hatch project
attempts to give researchers the means to visualize and explore their data before attempting
comprehensive processing and testing.  The ability to do this from a remote location via a
web interface, combined with an inherently scalable design, means that a central processing location 
can be scaled transparently to allow more complex visualizations, data transformations, and
forms of scientific analysis.

This tool is designed to work with general data sets, so any project that needs to filter, 
visualize, or transform data can make use of it.  It has been built to support ecological data sets 
without specifically adding functionality that will not apply to other types of data.

\setcounter{page}{1}

\pagebreak

%\input{reportSumm.tex} % - this stuff is ok, but I think the proposal stuff is better
\include{reportSumm}
%\include{reportSoftware.text} %should include what technologies we use; rails, couchdb, etc
\include{reportDatabase}
\include{reportSearch}
\include{reportVizualization}
\include{reportConclusion}
\include{reportRefs}
%\printglossaries



\end{document}
