\subsection{Visualization - Requirements}
\label{sec:viz_spec}
The Visualization controller is referred to throughout documentation simply as
\textbf{Viz}. It will be Rails 3 \textbf{views} and \textbf{controllers},
without models, since it mainly inteprets data from the Metadata
\ref{sec:metadata_spec} and Data I/O \ref{sec:data_io_spec} scaffolds. There 
will be one view per controller method, unless stated otherwise.

\subsubsection{Graphs - Types}
Viz graph types will be the following:
\begin{enumerate}
	\item line (default)
	\item bar
	\item scatterplot
	\item pie
	\item more (optional, future; i.e. statistical graphs)
\end{enumerate}

When a view/controller method gets data and no graph type argument, it will use
the default type. Otherwise, it will use the specified type.

\subsubsection{Data sets - Types}
Viz will graph the following data types natively on either x or y axis:
precedence:
\begin{enumerate}
	\item Date / time (may be combined):
	\begin{enumerate}
		\item time
		\item date
		\item timestamp
		\item datetime
	\end{enumerate}
	\item Chunkified data (see Section \ref{sec:data_types}):
	\begin{enumerate}
		\item boolean
		\item binary
		\item string
		\item text
	\end{enumerate}
	\item decimal
	\item float
	\item integer
\end{enumerate}

\subsubsection{Views - Show}
	\begin{enumerate}
		\item Viz will contain one show view. 
		\begin{enumerate}
			\item \textit{Verify that there is a Show view.}
		\end{enumerate}

		\item Some other controller will pass a Data model id and 
			two column names to graph data by.
		\begin{enumerate}
			\item \textit{Verify that this view graphs the 
				correct data for the Data id and two 
				columns listed.}
		\end{enumerate}

		\item The first passed column will be \textbf{x\_data} 
			in POST, the second will by \textbf{y\_data} in 
			POST, for the respective axis.
		\begin{enumerate}
			\item \textit{Verify that the respective columns 
				graph on the correct axis.}
		\end{enumerate}

		\item Controllers may pass a graph type, but if not,
			the default type will be used.
		\begin{enumerate}
			\item \textit{Verify that the 
				data is graphed in the correct graph types.}
		\end{enumerate}

	\end{enumerate}

\subsubsection{Views - Summary}
	\begin{enumerate}
		\item Viz will contain one Summary view. This view will take in a Data model data\_id POST value, and graph every unique permutation of two columns. 
		\begin{enumerate}
			\item Verify that the Summary view graphs the correct data for data\_id.
		\end{enumerate}

		\item There will be two Summary graphs per display row.
		\begin{enumerate}
			\item Verify that there are two Summary graphs per display row.
		\end{enumerate}

		\item Summary graphs will graph 10\% or 100 points of the data, whichever is bigger.
		\begin{enumerate}
			\item Verify that Summary graphs graph 10\% or 100 points of the data.
		\end{enumerate}

		\item Summary graphs will graph any type of data as defined in Data Types (Section \ref{sec:data_types}).
		\begin{enumerate}
			\item Verify Summary graphs graph any Data Type.
		\end{enumerate}

		\item 
		\begin{enumerate}
			\item 
		\end{enumerate}

	\end{enumerate}
